%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Software Engineer} % Job title
    {Amazon Web Services} % Organization
    {Dublin, Ireland} % Location
    {Apr. 2022 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing MessageBus(Java + Rust) for AWS DynamoDB, for handling very high network traffics.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer II} % Job title
    {Microsoft} % Organization
    {Shanghai, China} % Location
    {Nov. 2021 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing MCAT(Microsoft Compliance Assessment Toolkit) front-end UI, writing high quality code in JavaScript.}
        \item {Developing MCAT backend service API with ASP .NET for handling HTTP requests.}
      \end{cvitems}
    }


%---------------------------------------------------------
 \cventry
    {Radio Software Engineer} % Job title
    {Ericsson} % Organization
    {Stockholm, Sweden} % Location
    {Dec. 2019 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactoring radio software code for better maintenance.}
        \item {Designed a common module for event‐driven use cases and implemented event-loop based on epoll and asynchronous callbacks.}
        \item {Optimized cache policy for faster driver initialization under multi‐threading environment.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Radio Software Engineer} % Job title
    {Ericsson} % Organization
    {Nanjing, China} % Location
    {June. 2018 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Customized embedded linux distributions using Yocto Project.}
        \item {Rewrote low-level driver code and implemented interrupt‐driven module for radio ASIC chips, with better performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {iOS Developer} % Job title
    {Fanruan Software Co., Ltd.} % Organization
    {Nanjing, China} % Location
    {Mar. 2016 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and deployed iOS application, designed and implemented UI components layout for iPhone and iPad.}
        \item {Optimized iOS application render performance using RunLoop and CADisplayLink.}
        \item {Wrote a plug‐in web store for the report designer, using Javascript.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
